\speculake: Hiding Malware in Speculative Execution

### 2018-05-07 paper/appendix_spasm.tex
quick typo fix

SPASM is a 6 bit instruction set that we have developed to make use of the 
speculative primitive investigated in this work. The instruction set uses two 
functional registers, PTR and VAL, and a stack. This instruction set has been 
designed to be emulated in x86 and x86-64 environments, though the emulator 
could be implemented to run on other systems.

>>>>

SPASM is a 6 bit instruction set that we have developed to make use of the 
speculative primitive investigated in this work. The instruction set uses two 
functional registers, PTR and VAL, and a stack. This instruction set has been 
designed to be emulated in x86 and x86\_64 environments, though the emulator 
could be implemented to run on other systems.
